---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
require(tidyverse)
```

# crosstabby

<!-- badges: start -->
<!-- badges: end -->

Crosstabby is a package built to streamline the pre-processing and analysis of survey data.

## Installation

You can install the released version of crosstabby from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("crosstabby")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("smchoong/crosstabby")
```
## Crosstabby example: extended crosstab functionality

Let's use crosstabby's main function, **`big_tabby()`**, to generate a simple crosstab and then a more extensive crosstab. 

Here's an example of how to pull a simple crosstab:

```{r example}
library(crosstabby)
row<-c("pres_approval")
col<-c("gender")
data<-nationscape_2020_excerpt

crosstabby::big_tabby(data, row, col, percent = TRUE)

```

Now, let's pull a more complex crosstab that uses weights:

```{r cars}
row<-c("pres_approval", "vote_2016", "right_track", "economy_better", "vote_2020")
col<-c("pid3", "ideo5", "household_gun_owner", "gender", "census_region", 
       "race_ethnicity", "household_income", "education")
data<-nationscape_2020_excerpt

crosstabby::big_tabby(data, row, col, wts = "weight", percent = TRUE) %>%
  head()
```

So here we have a larger scale crosstab with row variables broken down by a number of different demographic variables. We don't yet have column spanner labels added in to make the crosstab more readable but this is the minimum viable **`big_tabby()`** product.

You'll notice that the **`big_tabby()`** function removed the "household_income" variable because it exceeded the recommended number of response levels (less than or equal to 20 levels). To get around this QC within **`big_tabby()`**, we'll want to either recode the income variable into a grouped variable with fewer levels or simply remove it from our desired column variables before running the crosstab.

